Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-16 main.tex
Abstract

	\begin{abstract}

	\end{abstract}

@@

We would like to control a system in order to maximise an \textit{arbitrary} reward function $R$, e.g. non-convex, non-smooth. These happen naturally: combinatorial optimization such as scheduling, obstacle avoidance.
Critical industrial setting: we do not want to commit mistakes. 
In particular, this rules out shiny Deep RL etc.
The only way to avoid mistakes from the outset, when the system is first deployed, is to incorporate some kind of prior knowledge. In this work, we assume that the system dynamics are partially known: known structure of a parametrized system, with unknown parameters. This is realistic in the sense that most industrial applications to date have been relying on physical models and corresponding optimal controllers rather than machine learning. Here, instead of providing the whole model, its main parts  
Data driven scheme: as we interact and observe more data of the true system, we can estimate the parameters more accurately.
This estimated model could be use to derive the corresponding optimal control, but this is unsafe: model bias.
To address this, we want to perform robust estimation: not just a maximum likelihood model, but a whole high-confidence region where the true system is likely to lie.
Given this ambiguity set, how should we act? Given the critical setting, we do not want to be optimistic, and try to minimise some cumulative regret. Quite the contrary, we want to be cautious, safe, prepare for the worst and plan for the best. A robust control scheme. Minimax problem are hard to solve, especially since $R$ can be arbitrary. We cannot use traditional tools from the robust LQ control community (coarse-id control, system-level synthesis). Instead, we adopt a hierachical control architecture, controller selection: discrete choice of a driving maneuver, a short-term goal, whose execution is performed by a fixed low-level controller. It is true that the passage from continuous optimization to discrete optimization induces a suboptimality. However, it can be mitigated by using a more diverse controller basis. We are left with a sequential optimization problem with continuous states and discrete actions: tree-based planning algorithms. But not a point estimate, a whole confidence region. Hence, a two step procedure: robust prediction of the reachability set, which provides a conservative pessimistic reward to the planning algorithm.

@@

\section{Multi-model Extension}

@@

One of the major benefits of using the family of linear models compared to richer classes is that it enables to measure empirically the adequacy of the modelling assumptions to capture the observed signal,  and thus to raise an alert when the adequacy is too low.

We define the model adequacy for an observation $y$ at point $x$ of the modelling assumptions $(A, \phi)$ trained on history $\cD$.
A value of 1 indicates no mismatch, while a value of 0 indicates a strong mismatch.

@@

\begin{definition}[Robust sequence upper bounds] We define an upper-bound for the value of sequences of actions:
\begin{equation}
\label{eq:robust_sequence_ucb}
b_i^r(n)  \eqdef
\begin{cases}
\min_{m\in[1, M]} \sum_{t=0}^{d-1} \gamma^t R_t^m  + \frac{\gamma^d}{1-\gamma} &\text{if } i \in \mathcal{L}_n \text{ ;}\\
\max_{a\in\mathcal{A}} B_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n 
\end{cases}
\end{equation}
where $R_t^m$ is the reward obtained at step $t$ by following $i$ with dynamics $f^m$.
\end{definition}
An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.

>>>>

\begin{abstract}
	We study the adaptive control of a linear system with unknown parameters and arbitrary costs in a critical setting where failures are costly and should be prevented at all time. We build on two ideas. First, we incorporate prior knowledge of the dynamics in the form of a known structure of uncertainty, that can be tightened as we collect interaction data by building high-confidence regions through least-square regression. Second, we act in a cautious way with respect to this uncertainty by formulating a robust objective, that we solve approximately in a prediction-optimisation manner, leveraging tools from interval prediction and tree-based planning. Additionally, we relax our modelling assumptions by proposing an extension based on multi-model selection and aggregation. The full procedure is designed to produce reasonable and safe behaviour at deployment, get more aggressive with time, and be asymptotically optimal. We illustrate it on a practical case of autonomous driving at an intersection.
\end{abstract}

@@

We would like to control a system in order to maximise an \textit{arbitrary} bounded reward function $R$, e.g. non-convex, non-smooth. These happen naturally: combinatorial optimization such as scheduling, obstacle avoidance.
Critical industrial setting: we do not want to commit mistakes. 
In particular, this rules out shiny Deep RL etc.
The only way to avoid mistakes from the outset, when the system is first deployed, is to incorporate some kind of prior knowledge. In this work, we assume that the system dynamics are partially known: known structure of a parametrized system, with unknown parameters. This is realistic in the sense that most industrial applications to date have been relying on physical models and corresponding optimal controllers rather than machine learning. Here, instead of providing the whole model, its main parts  
Data driven scheme: as we interact and observe more data of the true system, we can estimate the parameters more accurately.
This estimated model could be use to derive the corresponding optimal control, but this is unsafe: model bias.
To address this, we want to perform robust estimation: not just a maximum likelihood model, but a whole high-confidence region where the true system is likely to lie.
Given this ambiguity set, how should we act? Given the critical setting, we do not want to be optimistic, and try to minimise some cumulative regret. Quite the contrary, we want to be cautious, safe, prepare for the worst and plan for the best. A robust control scheme. Minimax problem are hard to solve, especially since $R$ can be arbitrary. We cannot use traditional tools from the robust LQ control community (coarse-id control, system-level synthesis). Instead, we adopt a hierachical control architecture, controller selection: discrete choice of a driving maneuver, a short-term goal, whose execution is performed by a fixed low-level controller. It is true that the passage from continuous optimization to discrete optimization induces a suboptimality. However, it can be mitigated by using a more diverse controller basis. We are left with a sequential optimization problem with continuous states and discrete actions: tree-based planning algorithms. But not a point estimate, a whole confidence region. Hence, a two step procedure: robust prediction of the reachability set, which provides a conservative pessimistic reward to the planning algorithm.

@@

\section{Multi-model Aggregation}

@@

One of the major benefits of using the family of linear models, compared to richer model classes, is that it enables to measure empirically the adequacy of the modelling assumptions to capture the observed signal, and thus to raise an alert when the adequacy is too low.

We define the model adequacy for an observation $y$ at point $x$ of the modelling assumptions $(A, \phi)$ trained on history $\cD$ by:
\begin{equation*}
    \alpha(y,x)
\end{equation*}
A value of 1 indicates no mismatch, while a value of 0 indicates a strong mismatch.

@@

\begin{definition}[Robust sequence upper bounds] We define an upper-bound for the value of a sequences of action $a$:
\begin{equation}
\label{eq:robust_sequence_ucb}
B_a^r(n)  \eqdef
\begin{cases}
\min_{m\in[M]} \sum_{t=0}^{h-1} \gamma^t R_t^m  + \frac{\gamma^h}{1-\gamma} &\text{if } a \text{ is a leaf;}\\
\max_{b\in\mathcal{A}} B_{ab}^r(n) & \text{else.}
\end{cases}
\end{equation}
where $R_t^m$ is the reward obtained at step $t$ by following $a$ with dynamics $f^m$.
\end{definition}
An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.
